### 2015-12-02 paper.tex
Move comment to issue #26

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/cp_curves}
\caption{{\bf Power Coefficient Curves.}
Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}

\textbf{\textit{[This figure shows that we haven't achieved Re independence (close though). I am sure many others will notice this.  Need to state why we couldn't go over Re = 1.3E6. I presume due to technical limitation.]}}
\label{fig:cp-curves}
\end{figure}

@@

The behavior of the power coefficient at $\lambda=3.1$ is plotted in
Fig.~\ref{fig:cp-re-dep}, where once again the increase in $C_P$ with $Re$ is
highlighted. We see that the power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$ \textbf{\textit{[define Rec]}},
beyond which there appears to be a small, linear, positive trend \textbf{\textit{[dCP/dRe seems to increase again for the two points: second and third highest Cp - any suggestion for the cause of this?  On a second thought, I think it's more appropriate to plot Re Vs. max Cp here ( don't fix TSR to 3.1, but pick a value which gives max Cp]}} . The tendency
of $C_P$ to continue increasing slightly could be an effect of lower virtual
camber \textbf{\textit{[I think we need to elaborate more on this. On its own, this sentence sounds very speculative]}} when compared to the strong $Re$-independence of the higher $c/R$
UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.

>>>>

\begin{figure}[h]
\includegraphics[width=\textwidth]{figures/cp_curves}
\caption{{\bf Power Coefficient Curves.}
Mean rotor power coefficient plotted versus mean tip speed ratio for multiple
Reynolds numbers.}
\label{fig:cp-curves}
\end{figure}

@@

The behavior of the power coefficient at $\lambda=3.1$ is plotted in
Fig.~\ref{fig:cp-re-dep}, where once again the increase in $C_P$ with $Re$ is
highlighted. We see that the power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \approx 2 \times 10^5$ \textbf{\textit{[define Rec]}},
beyond which there appears to be a small, linear, positive trend. The tendency
of $C_P$ to continue increasing slightly could be an effect of lower virtual
camber \textbf{\textit{[I think we need to elaborate more on this. On its own, this sentence sounds very speculative]}} when compared to the strong $Re$-independence of the higher $c/R$
UNH-RVAT \cite{Bachant2015-RVAT-Re-dep}.
